Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-12 paper-2024-sac-marl-neighbouring-strategies.tex
add conclusions

\section{Conclusion}\label{sec:conclusion}
\begin{itemize}
\item Summarize the key findings of the paper.
\item Emphasize the viability of neighbor-based methods as alternatives to centralized training in MARL.
\item Discuss the trade-offs observed in terms of performance, scalability, and communication overhead.
\item Suggest potential directions for future research, such as exploring hybrid approaches or more advanced communication protocols.
\end{itemize}

>>>>

\section{Conclusion}\label{sec:conclusion}
This paper proposes several neighbor-based strategies to achieve decentralized multi-agent learning (i.e., DTDE )with performance 
 comparable to centralized approaches (i.e., CTDE). 
%
These strategies offer the flexibility of DTDE while retaining the stability and performance of CTDE. 
%
Specifically, we introduce three approaches, namely: NN Averaging, NN Consensus and Experience Sharing
 which have been evaluated against various baselines, including CTDE, DTDE based on DQN, and MAPPO. 
%
The results show that two of the three proposed methods significantly enhance DTDE performance, achieving outcomes comparable 
 to CTDE, while NN consensus falls short of this goal, maintaining performance similar to DTDE. 
%
Furthermore, we analyzed the communication overhead, demonstrating that it remains minimal across all cases, 
 particularly with experience sharing, making it suitable for scenarios with very limited communication resources.

Future works may include several promising directions, namely:
\begin{enumerate*}[label=(\roman*)]
  \item explore the implementation of more advanced consensus algorithms to determine if this strategy can also achieve 
   results comparable to the other two;
  \item develop more sophisticated communication protocols to further reduce communication overhead; and
  \item test these approaches in a wider range of, and more complex, scenarios than the one considered in this paper.
\end{enumerate*}
